Cognate beginnings to bilingual lexical acquisition

### 2023-07-26 docs/index.qmd
Update Dockerfile

```{r setup}
#| label: setup
#| message: false
#| warning: false
# load objects -----------------------------------------------------------------
targets::tar_config_set(store = here::here("_targets"),
                        script = here::here("_targets.R"))

@@

title <- yaml_metadata$title
abstract <- yaml_metadata$abstract
thanks <- yaml_metadata$thanks
```

@@

```{r tbl-items}
participants |> 
    head(15) |> 
    glimpse()
```

@@

```{r tbl-items}
responses |> 
    head(15) |> 
    glimpse()
```

>>>>

```{r setup}
#| label: setup
#| message: false
#| warning: false
# load objects -----------------------------------------------------------------
targets::tar_config_set(
    store = here::here("_targets"),
    script = here::here("_targets.R")
)

@@

title <- yaml_metadata$title
abstract <- yaml_metadata$abstract
thanks <- yaml_metadata$thanks

targets::tar_load(items)
targets::tar_load(participants)
targets::tar_load(responses)

library(dplyr)
library(tidyr)
library(knitr)

```

@@

```{r tbl-participants}
participants |>
    head(15) |>
    glimpse()
```

@@

```{r tbl-responses}
responses |>
    head(15) |>
    glimpse()
```
